---
title: "ETC5242 Assignment 1"
subtitle: "Group 42"
author: "Khuyen Nguyen: kngu0086@student.monash.edu, Evan Ginting: , Rachitha Werake: "
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  tidy.opts = list(width.cutoff = 60),
  tidy = TRUE
)
```

```{r loading-data}
library(broom)
library(gridExtra)
library(kableExtra)
library(MASS)
library(tidyverse)
grades <- read_csv("data/GradesData.csv")
```

# Task 1 - fit a distribution [30 marks]
### The lecturer wants to examine “genuine” (non-zero) attempts only. Check and modify the data (if necessary) to ensure that only genuine attempts are analysed. [1 mark]

```{r non-zero}
grades <- grades %>%
  filter(Total != 0)
```

### Traditionally Normal distributions have been used to model grade distributions. Plot your data and explain whether you think that this is good idea in this instance. [3 marks]

```{r density}
dist <- grades %>%
  ggplot(aes(x = Total, y = after_stat(density))) +
  geom_histogram(colour = "blue",
                 fill = "blue",
                 alpha = 0.2) +
  geom_density(colour = "blue",
               fill = "blue",
               alpha = 0.2) +
  ggtitle("Distribution of Total Scores") +
  xlab("Total Score") +
  ylab("Density") +
  theme_bw()

dist
```

A normal distribution may be a good idea in this instance since the visualisation does resemble a bell shape. It is generally symmetric and unimodal. The distribution is slightly skewed, but overall, it can be a good fit.

### An alternative is the beta distribution. Explain why this may be a valid alternative in this case. [2 marks]

The beta distribution is also a viable option. To use it, we'll need to determine the parameter estimates $\alpha$ and $\beta$. Observing that the distribution shows a slight leftward tendency, the beta distribution may be well-suited for this situation. Additionally, since the test scores range from 0 to 1, the beta distribution's domain aligns with the data range.

### Use Maximum Likelihood to fit both a Normal and Beta distribution to the grades. Use a Bootstrap QQplot to assess the fit of each. Which distribution do you recommend? Be sure to briefly explain your reasoning. [8 marks]

**1. Normal distribution**

```{r normal-distribution, warning=FALSE}
fit_norm <- fitdistr(grades$Total, "normal")
fit_norm %>% tidy()
```

```{r norm-qqplot}
x <- grades$Total
n <- nrow(grades)
scores <- tibble(id = 1:n, x = x)
params_norm <- fit_norm$estimate

qq_norm <- ggplot(scores, aes(sample = x)) +
  stat_qq(distribution = qnorm, dparams = params_norm) +
  stat_qq_line(distribution = qnorm,
               dparams = params_norm,
               color = "black") +
  theme(aspect.ratio = 1) + theme_bw() +
  ggtitle("QQ plot of Total Scores according to a Normal Distribution") +
  xlab("Theoretical Distribution") + ylab("Total Scores")
```

```{r norm-bootstrap, warning=FALSE}
set.seed(474)

B <- 500

MLE.x_boot <- matrix(rep(NA, 2 * B), nrow = B, ncol = 2)
for (i in 1:B) {
  temp <- sample(grades$Total, size = n, replace = TRUE)
  scores <- scores %>% mutate(temp = temp)
  MLE.x_boot[i, ] <- fitdistr(temp, "normal")$estimate
  params_boot <- MLE.x_boot[i, ]
  qq_norm <-
    qq_norm + stat_qq(
      aes(sample = temp),
      distribution = qnorm,
      dparams = params_boot,
      colour = "grey",
      alpha = 0.2
    )
}
qq_norm <- qq_norm + stat_qq(aes(sample = x), distribution = qnorm,
                             dparams = params_norm) +
  ggtitle("QQ plot of Total Scores with B=500 Bootstrap replicates") 

qq_norm
```

**2. Beta distribution**

```{r beta-distribution, warning=FALSE}
fit_beta <- fitdistr(grades$Total, "beta", start = list(shape1 = 1, shape2 = 1))
fit_beta %>% tidy()
```

```{r beta-qqplot}
scores2 <- tibble(id = 1:n, x = x)
params_beta <- fit_beta$estimate

qq_beta <- ggplot(scores2, aes(sample = x)) +
  stat_qq(distribution = qbeta, dparams = params_beta) +
  stat_qq_line(distribution = qbeta,
               dparams = params_beta,
               color = "black") +
  theme(aspect.ratio = 1) + theme_bw() +
  ggtitle("QQ plot of Total Scores according to a Beta Distribution") +
  xlab("Theoretical Distribution") + ylab("Total Scores")
```

```{r beta-bootstrap, warning=FALSE}
set.seed(474)

B <- 500

MLE.x_boot <- matrix(rep(NA, 2 * B), nrow = B, ncol = 2)
for (i in 1:B) {
  temp <- sample(grades$Total, size = n, replace = TRUE)
  scores2 <- scores2 %>% mutate(temp = temp)
  MLE.x_boot[i, ] <- fitdistr(temp, "beta", start = list(shape1 = 1, shape2 = 1))$estimate
  params_boot <- MLE.x_boot[i, ]
  qq_beta <-
    qq_beta + stat_qq(
      aes(sample = temp),
      distribution = qbeta,
      dparams = params_boot,
      colour = "grey",
      alpha = 0.2
    )
}
qq_beta <- qq_beta + stat_qq(aes(sample = x), distribution = qbeta,
                             dparams = params_beta) +
  ggtitle("QQ plot of Total Scores with B=500 Bootstrap replicates")

qq_beta
```

**3. Recommendation**
 
Based on the Bootstrap QQ plots, I would recommend using the Beta distribution. You can observe that the grey confidence intervals on the Beta distribution have fewer points deviating from the line compared to the Normal distribution. In the Normal distribution, points deviate at both the beginning and end of the line, whereas for the Beta distribution, the fit is only slightly off at the beginning.

### The lecturer is interested in trying the Beta distribution. Use your MLE’s to report the mean and the median of the grade distribution (recall that the mean is a function of the shape and rate parameters). Be sure to interpret these values. [4 marks]

```{r}
median <- qbeta(0.5, shape1=5.95, shape2=2.63)
```

The mean of the Beta distribution is given by the formula: $\text{E}(X) = \frac{\alpha}{\alpha+\beta}$. 

Given our shape and rate parameters were 5.95 and 2.63 respectively, our mean is: $E[X] = \frac{5.95}{5.95+2.63} = 0.693$.

The median of the Beta distribution is `r round(median, 3)`, confirming the slight left skew we mentioned earlier.

### Plot and interpret a 99% parametric bootstrap of the mean of the beta distribution (HINT: set warning=FALSE in your code chunk). Did the average quiz mark match the lecturer’s goal? [4 marks]

```{r}
########### the bootplot.f function ############ 
bootplot.f<- function(stat.boot, bins=50, a=.05){

df <- tibble(stat = stat.boot)
CI <- round(quantile(stat.boot, c(a/2, 1-a/2)),2)
p <- df %>% ggplot(aes(x=stat, y=after_stat(density))) + 
geom_histogram(bins=bins, colour="magenta", fill="magenta", alpha=0.2) + 
geom_density(fill="magenta", colour="magenta", alpha=0.2) +
geom_vline(xintercept = CI, colour = "magenta", linetype=5) +
theme_bw() 

p 
} 
######## end of bootplot.f function #######
```

```{r}
boot.LCI.alpha <- quantile(MLE.x_boot[, 1], c(0.005, 0.995))
boot.LCI.alpha
```


```{r}
boot.LCI.beta <- quantile(MLE.x_boot[, 2], c(0.005, 0.995))
boot.LCI.beta
```

```{r}
p_MLEboot.alpha <- bootplot.f(MLE.x_boot[, 1], bins = 100) +
ggtitle("Sampling distribution for MLE of alpha") +
xlab("MLE of alpha") +
theme(title = element_text(size = 8))
p_MLEboot.beta <- bootplot.f(MLE.x_boot[, 2], bins = 100) +
ggtitle("Sampling distribution for MLE of beta") +
xlab("MLE of beta") +
theme(title = element_text(size = 8))
grid.arrange(p_MLEboot.alpha, p_MLEboot.beta, ncol = 2)
```

```{r}
ttest <- t.test(x = grades$Total, mu = 0.70, conf.level = 0.99) %>%
tidy()

ttest %>% 
kable() %>% 
kable_styling(latex_options = "hold_position")
```

The parametric bootstrap confidence interval (CI) for alpha is [4.797, 7.740], and for beta is [2.108, 3.438].

The lecturer advised that the average mark would be approximately 70%, with most students falling within about 10% of that grade. 

We are 99% confident that the population value $\mu$ is contained within our 99% confidence interval of [0.665, 0.721].

Since $\mu$ lies between 0.665 and 0.721, it does cover the average mark of 70% and meets the lecturer's goal.

### Using the MLE’s, what is the estimated proportion of students within 15% of the average? According to the lecturer’s benchmark, what proportion would have failed? How many would get HD’s? [4 marks]

The lower and upper bounds of the 15% range are:

```{r}
lowerbound <- 0.693 - 0.15 
upperbound <- 0.693 + 0.15
```

```{r}
pbeta(upperbound, shape1=5.95, shape2=2.63) - pbeta(lowerbound, shape1=5.95, shape2=2.63)
```

This gives us a probability of 0.666, which means that we estimate that 66.6% of students will fall within 15% of the average.

According to the lecturer's benchmark, a student who scores below 60% is considered to have failed. We can use the `pbeta()` function to calculate the proportion of students who are expected to fail:

```{r}
pbeta(0.6, shape1=5.95, shape2=2.63)
```

This gives us a proportion of 0.254, which means that we estimate that 25.4% of students will fail.

To calculate the number of students who are expected to get HD's, 

```{r}
(1 - pbeta(0.8, shape1=5.95, shape2=2.63))*193
```
51 students are expected to get HD's.

### Overall, do you think that the quiz achieved the lecturer’s aims? [4 marks]

Overall, I would say that the quiz achieved the lecturer's aims. The average mark fell around 70%, which is within the range that was expected for the lecturer. Additionally, 66.6% of students scored within 15% of the MLE mean of the grades, which suggests that the quiz was fair and that students were able to demonstrate their understanding of the material. However, the benchmark of 60% could be considered quite high, as 25.4% of the class failed. This suggests that the quiz may have been too difficult for some students, and that the lecturer may want to reconsider the benchmark in the future.

## Task 2 - Are Postgrad students better? [30 marks]

### Create a new variable “Result” which contains the values “Pass” or “Fail” depending on the value of the variable Total, and add it to your dataframe. (Hint: If you have the MASS package loaded, the dplyr command select will not work. Add dplyr::before any select command in your code.) [4 marks]

```{r}
grades <- grades %>%
  mutate(Result = dplyr::case_when(
    Total < 0.6 ~ "Fail",
    Total >= 0.6 ~ "Pass"
  ))
```

### Report a table with the relevant proportions and discuss the result. [10 marks]

```{r}
grades1 <- grades %>%
  group_by(Result, Cohort) %>%
  tally() %>%
  ungroup()

grades2 <- grades1 %>% 
  pivot_wider(names_from = Result, values_from = n) 

grades3 <- grades2 %>% 
  mutate(Total = Fail + Pass) %>% 
  mutate(Prop = round(Pass/Total, digits=3)) %>%
  select(Cohort, Pass, Fail, Total, Prop) 

grades4 <- grades3 %>% 
  arrange(desc(row_number())) 

grades4 %>% 
  kable() %>% 
  kable_styling()
```
There are more students enrolled in the undergraduate cohort, with a higher number of students passing and failing than in the postgraduate cohort. However, there is a higher proportion of students who passed in the postgraduate cohort compared to the undergraduate cohort, with 82% passing compared to 68%.

### Conduct a permutation test with 5000 replications. Plot the sampling distribution of your test. [4 marks]



## Task 3 - Bayesian Analysis [33 marks]
