---
title: "ETC5242 Assignment 1"
subtitle: "Group 42"
author: "Khuyen Nguyen: kngu0086@student.monash.edu, Evan Ginting: , Rachitha Werake: rwer0002@student.monash.edu "
output: pdf_document
---

**REMEMBER TO ADD STUDENT E-MAIL ABOVE^ (remove this line once done)**

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  tidy.opts = list(width.cutoff = 60),
  tidy = TRUE
)
```

```{r loading-data}
library(tidyverse)
library(broom)
grades <- read_csv("data/GradesData.csv")
```

# Task 1 - fit a distribution [30 marks]
### The lecturer wants to examine “genuine” (non-zero) attempts only. Check and modify the data (if necessary) to ensure that only genuine attempts are analysed. [1 mark]

```{r}
grades <- grades %>%
  filter(Total != 0)
```

### Traditionally Normal distributions have been used to model grade distributions. Plot your data and explain whether you think that this is good idea in this instance. [3 marks]

```{r}
library(MASS)
x <- c(grades$Total)
normal_fit <- fitdistr(x, "normal")
normal_fit %>% tidy()


normpdf <- grades %>% ggplot(aes(x=x, y=after_stat(density))) +
  geom_histogram(colour="blue", fill="blue", alpha=0.2, bins=30) +
  geom_density(colour="green", fill="green", alpha=0.2)

normpdf
```


## Task 2 - Are Postgrad students better? [30 marks]

## Task 3 - Bayesian Analysis [33 marks]
